Coupling PDEs on 3D-1D domains with Lagrange multipliers

### 2019-12-07 benchmark.tex
update

Following operator preconditioning technique \cite{mardal2011preconditioning} we
use as preconditioners for \eqref{eq:problem1} and \eqref{eq:problem2} in the
conforming case the (approximate) Riesz mapping with respect to the inner products of
the spaces in which the two formulations were proved to be well posed.
In particular, the preconditioner for the Lagrange multiplier relies on
(the inverse of) the fractional Laplacian $-\Delta^{-1/2}$ on $\Gamma$ for
\eqref{eq:problem1_simple} and $\Lambda$ for \eqref{eq:problem2_simple}.
In both cases the fractional Laplacian was realized by spectral decomposition
\cite{kuchta2016preconditioners}.

>>>>

Following operator preconditioning technique \cite{mardal2011preconditioning} we
propose as preconditioners for \eqref{eq:problem1} and \eqref{eq:problem2} in the
conforming case the (approximate) Riesz mapping with respect to the inner products of
the spaces in which the two formulations were proved to be well posed.
In particular, the preconditioner for the Lagrange multiplier relies on
(the inverse of) the fractional Laplacian $-\Delta^{-1/2}$ on $\Gamma$ for
\eqref{eq:problem1_simple} and $\Lambda$ for \eqref{eq:problem2_simple}.
A detailed analysis of the preconditioners will be presented in a separate
work. We remark that in both cases the fractional Laplacian was here realized
by spectral decomposition \cite{kuchta2016preconditioners}.
